Simultaneous Elicitation of Scoring Rule and Agents Preferences for Robust Winner Determination

### 2020-01-17 draft.tex
title
paper ID
small changes

\input{ijcai_preamble} 
\author{ID: 2696}
%\author{Beatrice Napolitano$^1$\and Olivier Cailloux$^1$	\and  Paolo Viappiani$^{2}$
%	\affiliations $^1$ LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
%	\emails \{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr
%}
%Restoring page numbers as missing them out violates basic human rights of the reviewers. -- Olivier
\thispagestyle{plain}
\pagestyle{plain}

@@

\title{Robust Winner Determination and Simultaneous Elicitation of Scoring Rule and Agents Preferences}

@@

Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
Since scoring rules are additively decomposable, we can consider separately the contribution of each voter to the total score. Thus, we can write the actual regret of choosing $x$ instead of $y$ as
\[
s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)},
\]
and we can rewrite $\PMR$ as follows:
\begin{align*}
& \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] \\
& =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]. \\
\end{align*}
Note that in general the inner max depends on the weights chosen by the outer min.

@@

The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$.
Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
%, as it can't be optimal. 
\commentBN{Indeed, the maximum regret of an alternative is the maximum value among all the PMRs, so we already know that $\MR(x) \geq \PMR(x,y)$, which is greater than the current MR. Thus, x will never be selected as a winner in the minimizing step.} 
This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.

>>>>

\input{ijcai_preamble} 
\author{ID: 7094}
%\author{Beatrice Napolitano$^1$\and Olivier Cailloux$^1$	\and  Paolo Viappiani$^{2}$
%	\affiliations $^1$ LAMSADE, UMR 7243, CNRS and Universit\'e Paris Dauphine, PSL Research University, Paris, France\\ $^2$ LIP6, UMR 7606, CNRS and Sorbonne Universit\'e, Paris, France
%	\emails \{firstname.lastname\}@dauphine.fr, paolo.viappiani@lip6.fr
%}
%Restoring page numbers as missing them out violates basic human rights of the reviewers. -- Olivier
\thispagestyle{plain}
\pagestyle{plain}

@@

\title{Simultaneous Elicitation of Scoring Rule and Agents Preferences for Robust Winner Determination}

@@

Recall that, in the computation of $s(x; \profile, \w)$, $w_{v_j(x)}$ represents the score that $x$ obtains in the ranking $v_j$ (see Equation \ref{eq:srule}).
Since scoring rules are additively decomposable, we can consider separately the contribution of each voter to the total score. Thus, we can write the actual regret of choosing $x$ instead of $y$ as
\[
s(y; \profile,\w) - s(x; \profile, \w) = \sum_{j=1}^n w_{v_j(y)} - w_{v_j(x)},
\]
and we can rewrite $\PMR$ as follows:
\begin{align*}
& \PMR(x,y; \pprofile, W) = \max_{\w \in W} \max_{\profile \in C(\pprofile)} [ s(y; \profile,\w) - s(x; \profile,\w) ] \\
& =  \max_{\w \in W} \sum_{j=1}^{n} \max_{v_j \in C(\succ_j^p)} [w_{v_j(y)} - w_{v_j(x)}]. \\
\end{align*}
Note that in general the inner max depends on the weights chosen by the outer max.

@@

The max regret $\MR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$.
Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
%\commentBN{Indeed, the maximum regret of an alternative is the maximum value among all the PMRs, so we already know that $\MR(x) \geq \PMR(x,y)$, which is greater than the current MR. Thus, x will never be selected as a winner in the minimizing step.} 
This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.
